# Some Further Thoughts

## Marathon Kids

### Mean and correlation Results

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(datasauRus)
library(dplyr)
library(ggplot2)
data("datasaurus_dozen")
q1 <- datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarise(mean(x), mean(y), cor(x,y))
knitr::kable(q1)
```


# A picture is worth a thousand words (**or a dinosaur**)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(datasaurus_dozen, aes(x = x, y = y)) +
  facet_wrap(~ dataset, nrow = 3) +
  geom_point()
```

### Reference

Same Stats, Different Graphs: Generating Datasets with Varied Appearance and Identical Statistics through Simulated Annealing.  Matejka,  Fitzmaurice. Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems. May 2017. Pages 1290–1294. https://doi.org/10.1145/3025453.3025912.

# NFL, a class room application

## [Real data](https://github.com/nflverse/nflverse-data/releases/tag/pbp)

## [Chaos](https://www.sportingnews.com/us/nfl/news/nfl-fourth-down-conversion-chart-rate-by-distance/vofkeub6xwms6imajxqkfipp)

## [Chaos explained](https://www.nflfastr.com/articles/field_descriptions.html)

## [Just one person's thoughts](https://rpubs.com/afuecker/727520)

# Concluding Thoughts

## The Beginning,  Genesis 1 NIV

::: {.rmdimportant}

In the beginning God created the heavens and the earth.  Now the earth was formless and empty, darkness was over the surface of the deep, and the Spirit of God was hovering over the waters.

:::

## The Source of the tension?  Genesis 17

::: {.rmdimportant}

17 To Adam he said...

**“Cursed is the ground because of you;
    through painful toil you will eat food from it
    all the days of your life.
18 It will produce thorns and thistles for you,
    and you will eat the plants of the field.
19 By the sweat of your brow
    you will eat your food
until you return to the ground,
    since from it you were taken;
for dust you are
    and to dust you will return.”**
    
::: 

## All work is honorable to God -- especially **analytics**

::: {.rmdimportant}

Aspire to live quietly, and to mind your own affairs, and **to work with your hands**, as we instructed you, so that you may walk properly before outsiders and be dependent on no one.” (1 Thess. 4:9–10)

:::

- A Popeye's table cleaner
- Sunday morning server
- House cleaner
- Septic tank pumper
- An athlete player becoming "more" than an athlete 
- Bringing order to chaos
- DOT worker
- Medical scheduler

::: {.rmdimportant}

Analytics is order out of chaos; it's doing God's work, helping others, allowing for tangible pride, and working with your hands.

:::

## My current life verse

### The Message, Galatations 5:22-23

::: {.rmdimportant}


22-23 But what happens when we live God’s way? He brings gifts into our lives, much the same way that fruit appears in an orchard—things like affection for others, exuberance about life, serenity. We develop a willingness to stick with things, a sense of compassion in the heart, and a conviction that a basic holiness permeates things and people. We find ourselves involved in loyal commitments, not needing to force our way in life, able to marshal and direct our energies wisely.

::: 